\thetitle

### 2013-06-19 tfpie/tfpie.tex
section 2

At Northeastern, the College of Computer \& Information Science (CCIS)
requires a four course introductory sequence in the first year.  The
first semester features both a course on discrete mathematics and
 an introduction to programming following the \emph{How to Design
  Programs} curriculum.  The second semester follows with a course on
object-oriented programming and one featuring formal reasoning about
programs, both on paper and with the ACL2 theorem
prover~\cite{dvanhorn:Kaufmann2000ComputerAided}.

Subsequent to the first year, students take a wide variety of
follow-up courses, ranging from a required course in ``Object-oriented
design'' to architecture, operating systems, robotics, and programming
languages.  No standard language is used in these courses.

More significantly, Northeastern distinctively emphasizes experiential
education, with almost all Computer Science majors participating in a
6 month ``co-op'' internship after their third semester.  These co-ops
take place at a wide variety of companies, and while most students do
some software development, there is almost no uniformity beyond that.

@@

\noindent
We reuse all of these elements in our approach.

>>>>

At Northeastern, the College of Computer \& Information Science (CCIS)
requires a four course introductory sequence for Computer Science majors in the first year.  The
first semester features both a course on discrete mathematics and
 an introduction to programming following the \emph{How to Design
  Programs} curriculum.  The second semester follows with a course on
object-oriented programming and one featuring formal reasoning about
programs, both on paper and with the ACL2 theorem
prover~\cite{dvanhorn:Kaufmann2000ComputerAided}.

After the first year, students take a wide variety of
follow-up courses, ranging from a required course in ``Object-oriented
design'' to architecture, operating systems, robotics, and programming
languages.  No standard language is used in these courses.

More significantly, Northeastern distinctively emphasizes experiential
education, with almost all Computer Science majors participating in a
6 month ``co-op'' internship after their third semester.  These co-ops
take place at a wide variety of companies, and while most students do
some software development, there is almost no uniformity beyond that.
In particular, there is wide variation in the languages students use
while on co-op.

@@

\noindent
We deliberately reuse all of these elements in our approach.
